\vspace{-2.0cm}The effect of nitrogen application time on infection and development of the Wheat Streak Mosaic Virus (WSMV)

### 2015-10-20 leslieandkenny.Rnw
More reorganization

\noindent If information about the physical layout of the field is
available, it would be possible to construct a similar heatmap to look
for spatial patterns. If correlation between nearby plots is seen,
the model should be modified to account for this. \\

\noindent Another option for examining the data graphically is the
\verb|itableplot| function in the \verb|tabplot| package. This is a
useful interactive tool for visualizing large datasets and identifying
patterns.

\begin{figure}[h!]
\caption{Example \texttt{itableplot} output.}
<<tabplot,echo=FALSE,warning=FALSE,message=FALSE>>=
# Tableplot is confusing. Maybe omit this?
fert.sim1$v.trt <- with(fert.sim1, interaction(status2, n.trt, variety))
tableplot(fert.sim1, select = c(infected, variety, block, n.trt, status, v.trt),
          nBins = 30, sortCol = "v.trt")
@
\end{figure}

@@

@@

# Now with plot-level REs
cbind(coef(glmQBin)[c(1,7:13,34:55)], fixef(glmmVar))
cbind(arm::se.coef(glmQBin)[c(1,7:13,34:55)], arm::se.fixef(glmmVar))
# Pretty similar. Maybe this is ok?
# Mark doesn't like it.
@

>>>>

\noindent If information about the physical layout of the field is
available, it would be possible to construct a similar heatmap to look
for spatial patterns. If correlation between nearby plots is seen,
the model should be modified to account for this.

@@

\subsection{Comparison of the GLM and the GLMM}

@@

# Now with plot-level REs
cbind(coef(glmQBin)[c(1,7:13,34:55)], fixef(glmmVarPlot))
cbind(arm::se.coef(glmQBin)[c(1,7:13,34:55)], arm::se.fixef(glmmVarPlot))
# Pretty similar. Maybe this is ok?
# Mark doesn't like it.
@
